State of the Art Review on Privacy-Preserving Authentication

### 2021-11-30 prism-backend/research/soa_review/app-ac.tex
Added review of Evernym.

\subsection{TODOs}

\subsection{Approaches, Models, and Variations}

@@

\paragraph{Efficiency.}

@@

\paragraph{Main challenges.}

\subsection{Related Primitives}

@@

\subsection{Applications}
\label{ssec:acapplication}

@@

\subsection{TODO}

@@

>>>>

\subsection{Academic Literature Review}

\subsubsection{Approaches, Models, and Variations}

@@

\subsubsection{Efficiency.}

@@

\subsubsection{Main challenges.}

\subsubsection{Related Primitives}

@@

\subsubsection{Applications}
\label{ssec:acapplication}

@@

\subsubsection{TODO}

@@

\subsection{Industry Systems Review}
\item Evernym. \url{https://www.evernym.com/}
  \item {\bf Introduction}. Evernym is a software company that is some kind of
    relative of Sovrin. Their solution builds completely on the Sovrin system.
  \item \emph{``How Sovrin Works''}%
    \footnote{\url{https://www.evernym.com/wp-content/uploads/2017/07/How-Sovrin-Works.pdf}}.
    Describes from a high-level perspective what information the Sovrin system
    manages, how it does it, and the main actors. Basically, it is a public and
    permissioned blockchain, that stores DIDs and VC schemas.
    %
    Some interesting properties (\textbf{Note: the following is based on
      whitepapers from 2016!}):
    \item Credentials/claims are multi-show.
    \item The keys used by issuers to produce claims can be rotated. To ensure
      that verifiers will be able to check credentials that have been issued
      with a rotated key, old keys are saved. This ``backward compatibility''
      is an interesting feature for real-world systems to consider.      
    \item Relationships between users and verifiers are not private:
      \emph{``Jane has a relationship with a retailer (we can tell since they
        have her verification key)''}
    \item Consent receipts: A kind of ``policy'' that is stored in the ledger,
      which contains the agreements reached between users and service providers
      (e.g., SP can use Alice's data to do X or Y, only during 30 days). The
      user can resort to the ledger to track past agreements.      
    \item Support for public and private attributes. Public attributes are/can
      be stored in the Sovrin ledger. Private attributes are stored in each
      user's private ledger: \emph{``One important purpose of the private ledger
        is to track the time and order that things are written. Hashes of the
        private ledger can be written to Sovrin's public ledger periodically to
        provide evidence of Jane's holdings. These are called anchors. Jane can
        thus generate audit proofs that any particular interaction happened at a
        particular time without disclosing the details of the interaction.''}
      Private ledgers can be managed by agencies, but they should be easily
      exportable to avoid lock-in.
  \item \emph{``The Technical Foundations of Sovrin.''}%
    \footnote{\url{https://www.evernym.com/wp-content/uploads/2017/07/The-Technical-Foundations-of-Sovrin.pdf}}.
    Describes from a high-level perspective the architecture of the system,
    mostly focusing on the blockchain network, and related components (like
    agents and clients). Some identity-related stuff:
    \item To create a new identity from scratch, users have to rely on ``trust
      anchors'' (i.e., participants of the network that have somehow acquired
      trust). The new user perform a kind of issuance protocol with this trust
      anchor, who endorses the new user by registering some information in the
      ledger. The user can check the trustworthiness of the anchor, and result
      of the registration, via the ledger. The described process (page 14)
      resembles the join-issue protocols in GSs and ACs.      
    \item Brief mention is made to public and private attributes (in page 20),
      which again are differentiated depending on whether they are: stored in
      the ledger (public), no matter if they are encrypted/obfuscated or not;
      or in a private ledger (private). %
      The document also mentions five types of claims: cleartext claims,
      encrypted claims, hash signature claims, proof of existence claims, and
      anonymous credentials. See page 21, although it barely gives an
      intuition.      
  \item \emph{``Why the Verifiable Credentials Community Should Converge on BBS+''}%
    \footnote{\url{https://www.evernym.com/blog/bbs-verifiable-credentials/}}.
    This is a blog post by a cryptographer in Evernym, that describes the
    evolution of Evernym's approach. They initially targetted CL credentials,
    which they implemented for Sovrin/Indy. Then, they decided to migrate to
    BBS+, supporting predicates for proofs, and revocation. They seemed to fail.
    Later, MATTR restricted the approach to selective disclosure (not sure if
    revocation is included). This is useful to understand the confusion between
    the terms ZKP-CL vs JSON-LD BBS+. They are just historical: the former is the
    approach Indy adopted, and they have their own user base and formats;
    JSON-LD BBS+ is the approach of MATTR, which Evernym (the descendant of
    Sovrin/Indy) seems to be adopting too.
